
---
title: "OFF-SEN FCP Dashboard" 
author: "Evidence and Analysis Team"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill 
    horizontal_layout: fill 
---
  
  <style>
  
  .navbar {
    background-color:#00A33B;
      border-color:#00A33B;
  }

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
  background-color: #77BC1F;
    color: white;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: #77BC1F;
}
.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: #77BC1F;
}
.navbar-inverse .navbar-collapse,
.navbar-inverse .navbar-form {
  border-color: #77BC1F;
}


.nav .open > a, .nav .open > a:focus, .nav .open > a:hover {
  background-color: #77BC1F;
}

.nav > li > a:focus, .nav > li > a:hover {
  background-color: #77BC1F;
}

</style>

  
```{r setup, include=FALSE}

options(repos = "https://cran.r-project.org")

usePackage <- function(p)
{
  if (!is.element(p, installed.packages()[, 1]))
    install.packages(p, dep = TRUE)
  require(p, character.only = TRUE)
}

usePackage("plyr") 
usePackage("flexdashboard")
usePackage("readr")
usePackage("dplyr")
usePackage("ggplot2")
usePackage("readODS")
usePackage("magrittr")
usePackage("plotly")
usePackage("openxlsx")
usePackage("stringr")
usePackage("scales")
usePackage("tidyr")
usePackage("survey")
usePackage("tibble")
usePackage("knitr")
usePackage("kableExtra")
usePackage("scales")
usePackage("highcharter")
usePackage("sparkline")
usePackage("htmlwidgets")
usePackage("viridis")
usePackage("labeling")
usePackage("crosstalk")
usePackage("ellipsis")
usePackage("forcats")
usePackage("farver")

knitr::opts_chunk$set(echo = FALSE)

.libPaths("C:/Users/jb000299/AppData/Local/R/win-library/4.2") # you must run this before knitting - sorts out weird filepath issue with pandoc
#defra colours from branding document
#defra_colours <- c("#00A33B", "#FFCC00", "#D9262E", "#6D3075", "#FF9E16", "#007CBA", "#77BC1F", "#D51067", "#48af65")
defra_colours <- viridis(12)

input_file <- "C:/Users/jb000299/Downloads/20240619-data_for_dashboard.xlsx"

narrative_file<-"C:/Users/jb000299/Downloads/20240619-narrative_for_dashboard.xlsx"

```

1.12a Farming Investment Fund: FETF {data-navmenu="All Metrics" data-orientation=rows}
=====================================

Row {data-height=90}
-----------------------------------------------------------------------
### Title {.no-title}

```{r include=FALSE}
Narrative_FIF <- read.xlsx(narrative_file, "1.12a")

```

`r Narrative_FIF$title`

Row {data-height=90}
-----------------------------------------------------------------------
### Assessment {.no-title}

`r Narrative_FIF$statistic`

Row {data-height=700} 
-----------------------------------------------------------------------

### Farming Equipment and Technology Fund - Values, 17 May 2024 {data-width=500}
``` {r productivity_small-val code, echo=FALSE, warning = FALSE}

Grants <- read.xlsx(input_file, "1.12a")

FETF <-  Grants[which(Grants$Scheme == "FETF 2024: AH&W" | Grants$Scheme == "FETF 2024: Productivity" | Grants$Scheme == "FETF 2024: Slurry" | Grants$Scheme == "FETF 2023: AH&W" | Grants$Scheme == "FETF 2023: Productivity & Slurry" | Grants$Scheme == "FETF: Round One"),]

FETF <- FETF %>%
  mutate(Scheme = factor(Scheme, levels = c('FETF 2024: Productivity', 'FETF 2024: Slurry','FETF 2024: AH&W', 'FETF 2023: Productivity & Slurry', 'FETF 2023: AH&W', "FETF: Round One"))) %>%
  mutate(Measure = factor(Measure, levels= c('Budget', 'Approved', 'Paid')))

# Define hex codes for colors
colour_codes <- c("#E95E3E", "#5DC58A", "#1f58c2")

plt <- ggplot(FETF, aes(x=Scheme, y=Value, fill = Measure, text = paste("Scheme:", Scheme, "<br>", Measure, ": £", Value2, "<br>", "Status:", Status))) +
  geom_bar(position = "dodge",stat = "identity") + 
  theme_bw() +
  ylab("Value (£ millions)") +
  scale_fill_manual(values = colour_codes, name=NULL) +
  theme(plot.title = element_text(size = 10)) +
  scale_y_continuous(limits=c(0,75)) +
  scale_x_discrete(limits = rev, labels = function(x) str_wrap(x, width = 10))

ggplotly(plt, tooltip = "text") %>%   layout(hovermode = "x")


```


### Farming Equipment and Technology Fund - Application and Claims, 17 May 2024 {data-width=500}
``` {r productivity_small-app code2, echo=FALSE, warning = FALSE}

Grants <- read.xlsx(input_file, "1.12a2")

FETF <-  Grants[which(Grants$Scheme == "FETF 2024: AH&W" | Grants$Scheme == "FETF 2024: Productivity" | Grants$Scheme == "FETF 2024: Slurry" | Grants$Scheme == "FETF 2023: AH&W" | Grants$Scheme == "FETF 2023: Productivity & Slurry" | Grants$Scheme == "FETF: Round One"),]

FETF <- FETF %>%
  mutate(Scheme = factor(Scheme, levels = c('FETF 2024: Productivity', 'FETF 2024: Slurry','FETF 2024: AH&W', 'FETF 2023: Productivity & Slurry', 'FETF 2023: AH&W', "FETF: Round One"))) %>%
  mutate(Measure = factor(Measure, levels= c('Budget', 'OA Approved', 'FA Approved', 'Paid')))

# Define hex codes for colors
colour_codes2 <- c("#E95E3E", "#5DC58A", "#1f58c2")

plt <- ggplot(FETF, aes(x=Scheme, y=Value, fill = Measure, text = paste("Scheme:", Scheme, "<br>", Measure, ":", Value2, "<br>", "Status:", Status))) +
  geom_bar(position = "dodge",stat = "identity") + 
  theme_bw() +
  ylab("Number") +
  scale_fill_manual(values = colour_codes2, name=NULL) +
  theme(plot.title = element_text(size = 10)) +
  scale_y_continuous(limits=c(0,6500)) +
  scale_x_discrete(limits = rev, labels = function(x) str_wrap(x, width = 10))

ggplotly(plt, tooltip = "text") %>%   layout(hovermode = "x")


```

Row {data-height=150} {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Narrative and Insights

`r Narrative_FIF$narrative`

### Data Explainer

`r Narrative_FIF$explainer`

### Source

`r Narrative_FIF$source`

### Confidence

`r Narrative_FIF$confidence`

### Distribution

`r Narrative_FIF$distribution`


### Dates

`r Narrative_FIF$update_date`

1.12b Farming Investment Fund: Large Grants {data-navmenu="All Metrics" data-orientation=rows}
=====================================

Row {data-height=90}
-----------------------------------------------------------------------
### Title {.no-title}

```{r include=FALSE}
Narrative_FIF <- read.xlsx(narrative_file, "1.12b")

```

`r Narrative_FIF$title`

Row {data-height=90}
-----------------------------------------------------------------------
### Assessment {.no-title}

`r Narrative_FIF$statistic`

Row {data-height=700} 
-----------------------------------------------------------------------

### Farming Investment Fund: Large Grants - Value, 17 May 2024 {data-width=500}
``` {r productivity_large-val code, echo=FALSE, warning = FALSE}

Grants <- read.xlsx(input_file, "1.12b")

FTF <- Grants %>%
  mutate(Scheme = factor(Scheme, levels = c('Large Grants: Adding Value - Round One', 'Large Grants: Productivity - Round Two', 'Large Grants: Productivity - Round One','Large Grants: Slurry - Round Two', 'Large Grants: Slurry - Round One', 'Large Grants: Water - Round Two', 'Large Grants: Water - Round One'))) %>%
  mutate(Measure = factor(Measure, levels= c('Budget', 'OA Approved', 'FA Approved', 'Paid')))

# Define hex codes for colors
colour_codes <- c("#E95E3E", "#8E44AD", "#5DC58A", "#1f58c2")

plt <- ggplot(FTF, aes(x=Scheme, y=Value, fill = Measure, text = paste("Scheme:", Scheme, "<br>", Measure, ": £", Value2, "<br>", "Status:", Status))) +
  geom_bar(position = "dodge",stat = "identity") + 
  theme_bw() +
  ylab("Value (£ millions)") +
  scale_fill_manual(values = colour_codes, name=NULL) +
  theme(plot.title = element_text(size = 10)) +
  scale_y_continuous(limits=c(0,125)) +
  scale_x_discrete(limits = rev, labels = function(x) str_wrap(x, width = 10))

ggplotly(plt, tooltip = "text") %>%   layout(hovermode = "x")


```


### Farming Investment Fund: Large Grants - Applications and Claims, 17 May 2024 {data-width=500}
``` {r productivity_large-app code, echo=FALSE, warning = FALSE}
Grants <- read.xlsx(input_file, "1.12b2")

FTF <- Grants %>%
  mutate(Scheme = factor(Scheme, levels = c('Large Grants: Adding Value - Round One', 'Large Grants: Productivity - Round Two', 'Large Grants: Productivity - Round One','Large Grants: Slurry - Round Two', 'Large Grants: Slurry - Round One', 'Large Grants: Water - Round Two', 'Large Grants: Water - Round One'))) %>%
  mutate(Measure = factor(Measure, levels= c('Online Applications', 'Full Applications', 'Claims')))

colour_codes2 <- c("#5DC58A", "#3E8EC2", "#1f58c2")

#I reorder the scheme so the labels don't over lap with reorder(Scheme, desc(Scheme)
plt <- ggplot(FTF, aes(x= Scheme, y=Value, fill = Measure, text = paste("Scheme:", Scheme, "<br>", Measure, ":", Value2, "<br>",  "Status:", Status))) +
  geom_bar(position = "dodge", stat = "identity") + 
  theme_bw() +
  ylab("Number") +
  scale_x_discrete(limits = rev, labels = function(x) str_wrap(x, width = 10))+
  scale_fill_manual(values = colour_codes2, name=NULL) +
  theme(plot.title = element_text(size = 10), legend.title = element_blank()) +
 scale_y_continuous(limits=c(0, 2250))

ggplotly(plt, tooltip = "text") %>%   layout(hovermode = "x")
legend.key.height=unit(2, "cm")

```

Row {data-height=150} {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Narrative and Insights

`r Narrative_FIF$narrative`

### Data Explainer

`r Narrative_FIF$explainer`

### Source

`r Narrative_FIF$source`

### Confidence

`r Narrative_FIF$confidence`

### Distribution

`r Narrative_FIF$distribution`


### Dates

`r Narrative_FIF$update_date`
